CdGF_aucrf

### 2016-09-30 code/CdGF_AUCRF.Rmd
remove randomized validation from aucrf

ran_cv10f_aucs <- c()
ran_cv10f_all_resp <- c()
ran_cv10f_all_pred <- c()
for(j in 1:iters){
  set.seed(j)
  sampling <- sample(1:nrow(aucrf_data),nrow(aucrf_data),replace=F)
  ran_cv10f_probs <- rep(NA,nrow(aucrf_data))
  for(i in seq(1,nrow(aucrf_data),5)){
    train <- aucrf_data[sampling[-(i:(i+4))],]
    test <- ran_outcome_data[sampling[i:(i+4)],]
    set.seed(seed)
    temp_model <- AUCRF(Euth_Early~., data=train, pdel=0.99, ntree=500)
    ran_cv10f_probs[sampling[i:(i+4)]] <- predict(temp_model$RFopt, test, type='prob')[,2]
  }
  ran_cv10f_roc <- roc(ran_outcome_data$Euth_Early~ran_cv10f_probs)
  ran_cv10f_all_pred <- c(ran_cv10f_all_pred, ran_cv10f_probs)
  ran_cv10f_all_resp <- c(ran_cv10f_all_resp, ran_outcome_data$Euth_Early)
  ran_cv10f_aucs[j] <- ran_cv10f_roc$auc
}
ran_cv10f_roc <- roc(ran_cv10f_all_resp~ran_cv10f_all_pred)

#### plot rocs
par(mar=c(4,4,1,1))
plot(c(1,0),c(0,1), type='l', lty=3, xlim=c(1.01,0), ylim=c(-0.01,1.01), xaxs='i', yaxs='i', ylab='', xlab='')
plot(otu_euth_roc, col='black', lwd=2, add=T, lty=1)
plot(cv10f_roc, col='gray', lwd=2, add=T, lty=1)
plot(LOO_roc, col='blue', lwd=2, add=T, lty=2)
plot(LOcO_roc, col='purple', lwd=2, add=T, lty=3)
plot(ran_cv10f_roc, col='orange', lwd=2, add=T, lty=1)
plot(predict_random_roc, col='red', lwd=2, add=T, lty=3)
mtext(side=2, text="Sensitivity", line=2.5)
mtext(side=1, text="Specificity", line=2.5)
legend('bottomright', legend=c(sprintf('Out-Of-Bag (AUC: %.3g)',otu_euth_roc$auc),
                               sprintf('Leave-1 mouse-out (AUC: %.3g)',LOO_roc$auc),
                               sprintf('Leave-1 cage-out (AUC: %.3g)',LOcO_roc$auc),
                               sprintf('10-fold CV (AUC: %.3g)',cv10f_roc$auc),
                               sprintf('Random OOB (AUC: %.3g)',predict_random_roc$auc),
                               sprintf('Random 10-fold CV (AUC: %.3g)',ran_cv10f_roc$auc),
                               sprintf('OOB vs Leave-1-out: p=%.2g', roc.test(otu_euth_roc,LOO_roc)$p.value),
                               sprintf('OOB vs 10-fold CV: p=%.2g', roc.test(otu_euth_roc,cv10f_roc)$p.value)
),lty=c(1,2,2,1,3,1,0,0), lwd=2, col=c('black','blue','purple','gray','red','orange'), bty='n')
```

@@

# boruta feature selection
#set.seed(seed)
#Boruta(Euth_Early ~ ., data = Validate_early_euth_df, maxRuns = 200)

#create dataframe for random RF-classification
Validate_early_euth_df <- Predict_early_euth_df
set.seed(seed)
Validate_early_euth_df$Euth_Early <- sample(Predict_early_euth_df$Euth_Early)

# create RF model
set.seed(seed)
rf_random_aucrf <- AUCRF(Euth_Early ~ ., data = Validate_early_euth_df,
                              ntree = n_trees, pdel = 0.05, ranking = 'MDA')
otu_random_probs <- predict(rf_random_aucrf$RFopt, type = 'prob')
otu_random_roc <- roc(Validate_early_euth_df$Euth_Early ~ otu_random_probs[ , 2])

random_aucrf_data <- Validate_early_euth_df[,c('Euth_Early',rf_random_aucrf$Xopt)]

#### 10-fold Cross validated - 10 repetitions
cv10r_aucs <- c()
cv10r_all_resp <- c()
cv10r_all_pred <- c()
for(j in 1:iters){
  set.seed(j)
  sampling <- sample(1:nrow(random_aucrf_data),nrow(random_aucrf_data),replace=F)
  cv10r_probs <- rep(NA,nrow(random_aucrf_data))
  for(i in seq(1,nrow(random_aucrf_data),5)){
    train <- random_aucrf_data[sampling[-(i:(i+4))],]
    test <- random_aucrf_data[sampling[i:(i+4)],]
    set.seed(seed)
    temp_model <- AUCRF(Euth_Early~., data=train, pdel=0.99, ntree=500)
    cv10r_probs[sampling[i:(i+4)]] <- predict(temp_model$RFopt, test, type='prob')[,2]
  }
  cv10r_roc <- roc(random_aucrf_data$Euth_Early~cv10r_probs)
  cv10r_all_pred <- c(cv10r_all_pred, cv10r_probs)
  cv10r_all_resp <- c(cv10r_all_resp, random_aucrf_data$Euth_Early)
  cv10r_aucs[j] <- cv10r_roc$auc
}
cv10r_roc <- roc(cv10r_all_resp~cv10r_all_pred)

#### leave-one-out
LOOr_probs <- NULL
LOOr_probs <- sapply(1:nrow(random_aucrf_data), function(i){
 train <- random_aucrf_data[-i,]
  test <- random_aucrf_data[i,]
  set.seed(seed)
  temp_model <- AUCRF(Euth_Early~., data=train, pdel=0.99, ntree=500)
  LOOr_probs[i] <- predict(temp_model$RFopt, test, type='prob')[,2]
})
LOOr_roc <- roc(random_aucrf_data$Euth_Early~LOOr_probs)

#### leave-one-cage-out
LOcOr_df <- cbind(cage_id = Predict_df$cage_id, random_aucrf_data)
cage_list_random <- as.character(unique(LOcOr_df$cage_id))

LOcOr_probs <- NULL
LOcOr_probs <- sapply(1:length(cage_list_random), function(i){
  by_cage <- LOcOr_df$cage_id == cage_list_random[i]
  LOcO_predict <- select(LOcOr_df, -cage_id)
  train <- LOcO_predict[-by_cage,]
  test <- LOcO_predict[by_cage,]
  set.seed(seed)
  temp_model <- AUCRF(Euth_Early~., data=train, pdel=0.99, ntree=500)
  LOcOr_probs[[i]] <- predict(temp_model$RFopt, test, type='prob')[,2]
})
LOcOr_probs <- unlist(LOcOr_probs)
LOcOr_roc <- roc(random_aucrf_data$Euth_Early~LOcOr_probs)

#### plot rocs
par(mar=c(4,4,1,1))
plot(c(1,0),c(0,1), type='l', lty=3, xlim=c(1.01,0), ylim=c(-0.01,1.01), xaxs='i', yaxs='i', ylab='', xlab='')
plot(otu_random_roc, col='black', lwd=2, add=T, lty=1)
plot(cv10r_roc, col='gray', lwd=2, add=T, lty=1)
plot(LOOr_roc, col='blue', lwd=2, add=T, lty=2)
plot(LOcOr_roc, col='red', lwd=2, add=T, lty=2)
mtext(side=2, text="Sensitivity", line=2.5)
mtext(side=1, text="Specificity", line=2.5)
legend('bottomright', legend=c(sprintf('Out-Of-Bag (AUC: %.3g)',otu_random_roc$auc),
                               sprintf('Leave-1 mouse-out (AUC: %.3g)',LOOr_roc$auc),
                               sprintf('Leave-1 cage-out (AUC: %.3g)',LOcOr_roc$auc),
                               sprintf('10-fold CV (AUC: %.3g)',cv10r_roc$auc)),
#                               sprintf('OOB vs Leave-1-out: p=%.2g', roc.test(otu_random_roc,LOOr_roc)$p.value),
#                               sprintf('OOB vs 10-fold CV: p=%.2g', roc.test(otu_random_roc,cv10r_roc)$p.value)),
		lty=c(1,2,2,1,0,0), lwd=2, col=c('black','blue','red','gray'), bty='n')
```

### Add ranges to RF ROC

>>>>

#### plot rocs
par(mar=c(4,4,1,1))
plot(c(1,0),c(0,1), type='l', lty=3, xlim=c(1.01,0), ylim=c(-0.01,1.01), xaxs='i', yaxs='i', ylab='', xlab='')
plot(otu_euth_roc, col='black', lwd=2, add=T, lty=1)
plot(cv10f_roc, col='gray', lwd=2, add=T, lty=1)
plot(LOO_roc, col='blue', lwd=2, add=T, lty=2)
plot(LOcO_roc, col='purple', lwd=2, add=T, lty=3)
mtext(side=2, text="Sensitivity", line=2.5)
mtext(side=1, text="Specificity", line=2.5)
legend('bottomright', legend=c(sprintf('Out-Of-Bag (AUC: %.3g)',otu_euth_roc$auc),
                               sprintf('Leave-1 mouse-out (AUC: %.3g)',LOO_roc$auc),
                               sprintf('Leave-1 cage-out (AUC: %.3g)',LOcO_roc$auc),
                               sprintf('10-fold CV (AUC: %.3g)',cv10f_roc$auc),
                               sprintf('OOB vs Leave-1-out: p=%.2g', roc.test(otu_euth_roc,LOO_roc)$p.value),
                               sprintf('OOB vs 10-fold CV: p=%.2g', roc.test(otu_euth_roc,cv10f_roc)$p.value)
),lty=c(1,2,2,1,0,0), lwd=2, col=c('black','blue','purple','gray','red'), bty='n')
```

@@

# boruta feature selection
#set.seed(seed)
#Boruta(Euth_Early ~ ., data = Validate_early_euth_df, maxRuns = 200)
```

### Add ranges to RF ROC ??
